Finite Complete Suites for CSP Refinement Testing

### 2019-04-14 scp-journal/article-revision-1/main.tex
Changes w.r.t. remarks of reviewer #3

% -----------------------------------------------------------------------------
\paragraph{Minimal Hitting Sets of Minimal Acceptances} In this article, we are
interested in the minimal hitting sets of minimal acceptances; for these, the
abbreviated notation
$%\[ \
\minhits(P/s) = \minhits(\minaccs(P/s))
$ %\]
is used. The minimal hitting sets
of minimal acceptances may be alternatively characterised by means of the
failures of a process as is done in~\cite{DBLP:conf/icfem/CavalcantiG07}. To
this end, in~\cite{DBLP:conf/icfem/CavalcantiG07}, the authors define, for
any collection ${\cal C}\subseteq 2^\Sigma$ of subsets from $\Sigma$
\begin{equation}\label{eq:minsub}
\minsub({\cal C}) = \{ A\in {\cal C}~|~\forall B\in {\cal C}:
B\subseteq A\Rightarrow B = A \}.
\end{equation}
The collection $\minsub({\cal C})$ contains all those sets of
${\cal C}$ that are not true subsets of other members of ${\cal C}$. With
this definition, the relation between failures and minimal hitting sets of
minimal acceptances is established in the following lemma.
%
\begin{lemma}
\label{lemma:failureshittingsets}
For any trace $s$ of CSP process $P$, define
$%\[
{\cal A}_s = \{ A\subseteq \Sigma~|~(s,A)\not\in\fails(P)  \}.
$ %\]
Then
$ %\[
\minhits(P/s) = \minsub {\cal A}_s
$ %\]
for all traces $s$ of $P$.
\end{lemma}
\begin{proof}
We derive
\begin{argue}
(s,A)\not\in \fails(P)
\\
\Leftrightarrow A\not\in Ref(P/s)
\\
\Leftrightarrow  \forall R\in maxRef(P/s): A\not\subseteq R
\\
\Leftrightarrow   \forall B\in minAcc(P/s): A\not\subseteq (\Sigma\setminus
B)& this follows from (\ref{eq:accref})
\\
\Leftrightarrow  \forall B\in minAcc(P/s): A\cap B\neq \varnothing
\\
\Leftrightarrow  A \text{ is a (not necessarily minimal)}
              \text{ hitting set of } minAcc(P/s)
\end{argue}
%
Specialising this derivation valid for arbitrary $A$ satisfying $(s,A)\not\in {\text{failures}}(P)$ to
minimal $A$ with this property proves the statement of the lemma.
\xbox
\end{proof}

@@

It is assumed that the events $\efail$ and $\epass$, indicating verdicts FAIL
and PASS for the test execution, are not included in $\Sigma$. Since we
assume that $Q$ is free of livelocks, it is guaranteed that events $\efail$
or $\epass$ always become visible, if they are the only events $U_F(j)/s$ is
ready to engage in: if $U_F(j)/s$ can only produce $\epass$ or $\efail$, the
occurrence of these events can never be blocked due to a livelock in $Q$
occurring in the same step of the execution.

@@

Since we have finite complete CSP test suites, it is useful for the first
time to calculate how many test executions are needed when using them.
Previous work did not consider sufficient conditions for finiteness, so
complexity was not a concern. We answer the following questions. (1)~What is
the worst-case bound on the number of test executions to be performed to
verify an SUT with respect to failures refinement, when we use our test
suite? (2)~What is the worst-case bound for traces refinement? (3)~Is it
possible to reduce the maximal length of traces when testing for failures or
traces refinement? We consider the first question~(1) in
Section~\ref{section:complexity:failures}), where we also discuss whether it
it is possible to reduce the number of test executions with a different test
suite.  With the answer to question~(1), question~(2) is a fairly simple
consequence we discuss briefly also in
Section~\ref{section:complexity:failures}. Question~(3) is the subject of
Section~\ref{section:complexity:length}.

@@

Moreover, Theorem~\ref{th:sperner} establishes that given an alphabet with
$n$ elements, there is no Sperner family consisting of more than
$\binom{n}{\lfloor\frac{n}{2}\rfloor}$. In addition, we recall the minimal
hitting sets calculated from a given set of minimal acceptances are a Sperner
family~(see discussion in Section~\ref{sec:sperner}). So, (\ref{eq:pmaxd})
establishes that there is no possibility of providing more choices fom
minimal hitting sets with a test derived from a process different from
$\pmax$.

>>>>

% -----------------------------------------------------------------------------
\paragraph{Minimal Hitting Sets of Minimal Acceptances} In this article, we are
interested in the minimal hitting sets of minimal acceptances; for these, the
abbreviated notation
$%\[ \
\minhits(P/s) = \minhits(\minaccs(P/s))
$ %\]
is used. The minimal hitting sets
of minimal acceptances may be alternatively characterised by means of the
failures of a process as is done in~\cite{DBLP:conf/icfem/CavalcantiG07}. To
this end, in~\cite{DBLP:conf/icfem/CavalcantiG07}, the authors define, for
any collection ${\cal C}\subseteq 2^\Sigma$ of subsets from $\Sigma$
\begin{equation}\label{eq:minsub}
\minsub({\cal C}) = \{ A\in {\cal C}~|~\forall B\in {\cal C}:
B\subseteq A\Rightarrow B = A \}.
\end{equation}
The collection $\minsub({\cal C})$ contains all those sets of
${\cal C}$ that are not true supersets of other members of ${\cal C}$. With
this definition, the relation between failures and minimal hitting sets of
minimal acceptances is established in the following lemma.
%
\begin{lemma}
\label{lemma:failureshittingsets}
For any trace $s$ of CSP process $P$, define
$%\[
{\cal A}_s = \{ A\subseteq \Sigma~|~(s,A)\not\in\fails(P)  \}.
$ %\]
Then
$ %\[
\minhits(P/s) = \minsub {\cal A}_s
$ %\]
for all traces $s$ of $P$.
\end{lemma}
\begin{proof}
We derive
\begin{argue}
(s,A)\not\in \fails(P)
\\
\Leftrightarrow A\not\in Ref(P/s)
\\
\Leftrightarrow  \forall R\in maxRef(P/s): A\not\subseteq R
\\
\Leftrightarrow   \forall B\in minAcc(P/s): A\not\subseteq (\Sigma\setminus
B)& this follows from (\ref{eq:accref})
\\
\Leftrightarrow  \forall B\in minAcc(P/s): A\cap B\neq \varnothing
\\
\Leftrightarrow  A \text{ is a (not necessarily minimal)}
              \text{ hitting set of } minAcc(P/s)
\end{argue}
%
Specialising this derivation valid for arbitrary $A$ satisfying $(s,A)\not\in {\text{failures}}(P)$ to
minimal $A$ with this property proves the statement of the lemma.
\xbox
\end{proof}

@@

It is assumed that the events $\efail$ and $\epass$, indicating verdicts FAIL
and PASS for the test execution, are not included in $\Sigma$. Since we
assume that $Q$ is free of livelocks, it is guaranteed that events $\efail$
or $\epass$ always become visible, if they are the only events $U_F(j)/s$ is
ready to engage in: if $U_F(j)/s$ can only produce $\epass$ or $\efail$, the
occurrence of these events can never be blocked due to a livelock, since the only
  process executing concurrently with  $U_F(j)$  is livelock-free  $Q$.

@@

Since we have finite complete CSP test suites, it is useful for the first
time to calculate how many test executions are needed when using them.
Previous work did not consider sufficient conditions for finiteness, so
complexity was not a concern. We answer the following questions. (1)~What is
the worst-case bound on the number of test executions to be performed to
verify an SUT with respect to failures refinement, when we use our test
suite? (2)~What is the worst-case bound for traces refinement? (3)~Is it
possible to reduce the maximal length of traces when testing for failures or
traces refinement? We consider the first question~(1) in
Section~\ref{section:complexity:failures}, where we also discuss whether  
it is possible to reduce the number of test executions with a different test
suite.  With the answer to question~(1), question~(2) is a fairly simple
consequence we discuss briefly at the end of 
Section~\ref{section:complexity:failures}. Question~(3) is the subject of
Section~\ref{section:complexity:length}.

@@

Moreover, Theorem~\ref{th:sperner} establishes that given an alphabet with
$n$ elements, there is no Sperner family consisting of more than
$\binom{n}{\lfloor\frac{n}{2}\rfloor}$ members. In addition, we recall the minimal
hitting sets calculated from a given set of minimal acceptances are a Sperner
family~(see discussion in Section~\ref{sec:sperner}). So, (\ref{eq:pmaxd})
establishes that there is no possibility of providing more choices from
minimal hitting sets with a test derived from a process different from
$\pmax$.
